\bf\mftitle

### 2011-02-28 doc/jInfer/autoeditor/autoeditor.tex
Documentation: AutoEditor.

In case a generic class has a type parameter \code{T}, this has to be the same \code{T} that is used to parametrize jInfer automata. JUNG classes usually need a type parameter for a state and for an edge. These should be then \code{State\textless T\textgreater} (for a state) and \code{Step\textless T\textgreater} (for edge).

@@

New \code{Layout}s can be implemented using the modular system. For information on system of modules, see \cite{archdoc}. To create a new implementation of \code{Layout} interface, it is necessary to create a new class implementing \code{LayoutFactory} interface (package \code{package cz.cuni.mff.ksi.jinfer.autoeditor.automatonvisualizer.layouts}) and annotate it by the following code.

@@

@@

\begin{figure}
\centering\includegraphics[scale=\myscale]{uml_derived_classes}
\caption{Class diagram for the derived classes, not showing members of classes from figure \ref{uml_base_classes} to keep this diagram simple. Also not showing signatures of constructors of StatePickingVisualizer and StatePickingVisualizer for their length.} \label{uml_derived_classes}
\end{figure}

@@

\subsubsection{StatesPickingComponent} \label{subsubsection:StatesPickingComponent}
\begin{figure}
\centering\includegraphics[scale=0.6]{screenshot}
\caption{Screenshot of \jmodule{AutoEditor} GUI} \label{figure_gui}
\end{figure}

Classes \code{StatePickingComponent} and \code{StatesPickingVisualizer} are similar to the classes described in the previous section. Purpose of these is to provide picking of multiple automaton states.\\

@@

Signature of constructor and description of arguments follow.
\begin{verbatim}
public StatesPickingVisualizer(Layout<State<T>, Step<T>> layout, Transformer<Step<T>, String> edgeLabelTransformer)
\end{verbatim}
\begin{itemize}
	\item \code{layout} - Instance of \code{Layout} which will be provided to the constructor of parent \code{Visualizer} class.
	\item \code{edgeLabelTransformer} - Transformer to convert automaton edges to their string representations.
\end{itemize}

\code{StatesPickingComponent} is almost the same as \code{StatePickingComponent} but it contains two extra GUI controls. 'Continue' button and 'Don't ask me anymore to select states to be merger' checkbox.\
The button is supposed to be clicked when user picked all desired states and it will cause calling of component's \code{guiDone()} method (see \ref{subsubsection:AbstractComponent}).\
State of the checkbox can be retrieved by the calling code and the caller is supposed to stop showing this component in the current inference process.

@@

>>>>

In case a generic class has a type parameter \code{T}, this has to be the same \code{T} that is used to parametrize jInfer automata. JUNG classes usually need a type parameter for a state and for an edge. These should be then \code{State\textless T\textgreater} (for a state) and \code{Step\textless T\textgreater} (for edge). Refer to \cite{archdoc} for more information on these classes and see \ref{subsubsection:StatePickingComponent} and \ref{subsubsection:StatesPickingComponent} for source code examples.

@@

New \code{Layout}s can be implemented using the modular system. For information on system of modules, see \cite{archdoc}. To create a new implementation of \code{Layout} interface, it is necessary to create a new class implementing \code{LayoutFactory} interface (package \code{cz.cuni.mff.ksi.jinfer.autoeditor.automatonvisualizer.layouts}) and annotate it by the following code.

@@

\begin{figure}
\centering\includegraphics[scale=\myscale]{uml_derived_classes}
\caption{Class diagram for the derived classes, not showing members of classes from figure \ref{uml_base_classes} to keep this diagram simple. Also not showing signatures of constructors of StatePickingVisualizer and StatePickingVisualizer for their excessive length.} \label{uml_derived_classes}
\end{figure}

@@

@@

\subsubsection{StatesPickingComponent} \label{subsubsection:StatesPickingComponent}
Classes \code{StatePickingComponent} and \code{StatesPickingVisualizer} are similar to the classes described in the previous section. Purpose of these is to provide picking of multiple automaton states.\\

@@

Signature of constructor and description of arguments follow.
\begin{verbatim}
public StatesPickingVisualizer(
  Layout<State<T>, Step<T>> layout,
  Transformer<Step<T>, String> edgeLabelTransformer)
\end{verbatim}
\begin{itemize}
	\item \code{layout} - Instance of \code{Layout} which will be provided to the constructor of parent \code{Visualizer} class.
	\item \code{edgeLabelTransformer} - Transformer to convert automaton edges to their string representations.
\end{itemize}

\code{StatesPickingComponent} is almost the same as \code{StatePickingComponent} but it contains two extra GUI controls. 'Continue' button and 'Don't ask me anymore to select states to be merger' checkbox.\
The button is supposed to be clicked when user picked all desired states and it will cause calling of component's \code{guiDone()} method (see \ref{subsubsection:AbstractComponent}).\
State of the checkbox can be retrieved by the calling code and the caller is supposed to stop showing this component in the current inference process.\\

@@

\begin{figure}
\centering\includegraphics[scale=0.6]{screenshot}
\caption{Screenshot of \jmodule{AutoEditor} GUI} \label{figure_gui}
\end{figure}
